% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Joseph Voss}
\newcommand{\CVTitle}{Joseph Voss' Resume}
\newcommand{\CVNote}{Compiled on {\today}}
\newcommand{\CVWebpage}{http://josephvoss.com}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
{5610 Abilene Trail, Austin, TX 78749, USA}
\par
\href{\CVWebpage}
{\url{\CVWebpage}}
\,\SubBulletSymbol\,
(512)\,517-0468
\,\SubBulletSymbol\,
\href{mailto:josephvoss14@gmail.com}
{josephvoss14@gmail.com}

\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%
\BigGap

\Section
{Education}
{Education}
{PDF:Education}

\Entry
%\href{http://www.example.com/my-university}
{\textbf{Bachelor of Science, Mechanical Engineering}},
University of Texas at Austin
\hfill
\DatestampYMD{2014}{08}{25} --
\DatestampYMD{2018}{05}{04}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Experience}
{Experience}
{PDF:Experience}
\Entry

\href{http://olcf.ornl.gov}
{\textbf{HPC Systems Engineer, Oak Ridge National Laboratory}
  \hfill \DatestampYMD{2018}{06}{05} -- Present}
\Gap
\begin{Detail}
\BulletItem
Wrote custom tool to boot HPC machines from container images. Transitioned
  several large scale systems to use it.
\BulletItem
Created Helm charts and automated pipelines to move system services to
  Kubernetes
\BulletItem
Developed CI pipeline to stage Puppet changes on bare metal servers
\BulletItem
Reviewed proposals for new HPC Systems. Assisted in their provisioning and
  deployment.
\BulletItem
Extended Let's Encrypt Golang projects to create in-house certificate issuer for
  host authentication bootstrapping
\BulletItem
Managed 600 node HPC post processing cluster in transition to Slurm and GPFS
\BulletItem
Used Puppet to configure and manage large scale systems
\BulletItem
Contributed to open source projects to extend features needed to simplify our
  configuration
\BulletItem
Super short and sweet. Leveraged Puppet, Golang, Python, and Kubernetes to
  simplify management of HPC systems.

\end{Detail}

\BigGap 
\Entry
\href{http://multimechanics.com}
{\textbf{DevOps Engineer, MultiMechanics}
  \hfill
  \DatestampYMD{2018}{01}{21} --
  \DatestampYMD{2018}{05}{18} }
\Gap
\begin{Detail}
\BulletItem
Created automated build system using Vagrant. Converting software tools from
  Windows to Redhat and SUSE environments.
\BulletItem
Configured and installed pbs-pro job scheduler to better share computing
    \newline resources. Lead training on it's usage
\end{Detail}

\BigGap

\Entry
\href{http://tacc.utexas.edu}
{\textbf{Texas Advanced Computing Center}}

\Gap
\BulletItem
Student Intern, High Performance Computing
\hfill
\DatestampYMD{2017}{06}{01} --
\DatestampYMD{2017}{08}{25}
\begin{Detail}
\SubBulletItem
Developed an automated HPC testing harness using Jenkins, PyTest, and \newline
  CMake that integrates seamlessly with SLURM
\SubBulletItem
Created a heatmap visualization showing historical degradation \newline
  and improvement in system performance
\end{Detail}
\hfill
\DatestampYMD{2016}{02}{20} --
\DatestampYMD{2017}{03}{30}
\begin{Detail}
\SubBulletItem
Designed, built and managed a cluster of high performance compute nodes
\SubBulletItem
Developed remote power monitoring system using SNMP, Graphite, \newline and
  Grafana
\SubBulletItem
Learned how to use and profile several HPC applications
\SubBulletItem
Attended Supercomputing Conference 2016 to compete with student teams \newline
  from around the world, placed 4\textsuperscript{th} overall
\end{Detail}

\BigGap

\Entry
\href{http://arlut.utexas.edu}
{\textbf{Science and Engineering Apprentice, Applied Research Laboratory}
  \hfill
  \DatestampYMD{2014}{05}{20} --
  \DatestampYMD{2015}{08}{26}}
\begin{Detail}
\BulletItem
Created a suite of cross-compatible unit tests in C++ for open source software
\BulletItem
Redesigned the method of reading/writing out RINEX files to use OOP \newline
  encapsulation
\BulletItem
Developed an inexpensive COTS GPS data collection platform using \newline
  Python; decodes binary streams and writes out to a formatted RINEX file
\end{Detail}


%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
Python, 
Puppet,
Golang,
Openshift,
Bash,
Git, 
C++, 
Jenkins,
Linux management \& development, 
\LaTeX

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Publications %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Publications}
{Publications}
{PDF:Publications}

\Entry
\href{http://doi.acm.org/10.1145/3155105.3155106}
{\underline{Voss, J.}, Garcia, J. A., Proctor, W. C., \& Evans, R. T.
(2017). ``Automated System Health and Performance Benchmarking Platform."
In \textit{Supercomputing Conference '17: Proceedings of the 2nd international
HPC System Professionals Workshop at SC'17}. New York, NY, USA: ACM.
https://doi.acm.org/10.1145/3155105.3155106}
\Gap

\Entry
\href{https://doi.org/10.1016/j.parco.2017.07.002}
{Ababao, R., Garcia, J. A., \underline{Voss, J.}, Proctor, W. C., \& Evans, R.
T. (2017). ``Student Cluster Competition 2016 reproducibility challenge: Genomic
partitioning with ParConnect." \textit{Parallel Computing.}
https://doi.org/10.1016/j.parco.2017.07.002}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL ACHIEVEMENTS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \Section
% {Professional Achievements}
% {Professional Achievements}
% {PDF:ProfessionalAchievements}
% 
% \Entry
% Terry Foundation Scholar
% \hfill
% \DatestampY{2014} --
% Current
% 
% \Entry
% Presidential Achievement Scholar
% \hfill
% \DatestampY{2014} --
% Current
% 
% \Entry
% Eagle Scout, Troop 3
% \hfill
% \DatestampY{2012}

\end{Body}
\end{document}

%\Entry
%Member, Programmers in Science and Engineering
%\hfill
%\DatestampY{2016}--
%Current

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

%\UseNoteFont%
%\null\hfill%
%[\textit{\CVNote}]

